Hippocampal replay of experience at slow speeds

### 2021-04-28 Article.tex

One possibility is that these events are supported by different subcircuits within the hippocampus.For example, \cite{OlivaRoleHippocampalCA22016} showed that CA2 neurons tend to lead CA1 and CA3 neurons during SWRs. We did not have enough simultaneously recorded tetrodes in each area to attribute the different dynamics to particular subregions.

>>>>

One possibility is that these events are supported by different subcircuits within the hippocampus. For example, \cite{OlivaOriginGammaFrequency2018a} showed that layer 2/3 neurons in the entorhinal cortex increased their firing 50 ms before the start of longer duration SWRs (>100 ms), but not before the start of shorter duration SWRs, suggesting that

showed that CA2 neurons tend to lead CA1 and CA3 neurons during SWRs. We did not have enough simultaneously recorded tetrodes in each area to attribute the different dynamics to particular subregions. However, we did show that our result holds even if restricting the dataset only to CA1 tetrodes.
